\documentclass[11point]{article}
% set the margins
\usepackage[left=25mm,right=25mm,top=20mm,bottom=20mm]{geometry}
% for displaying images
\usepackage{graphicx}
% for equation support, e.g. eqref
\usepackage{amsmath}
% for table support, e.g. toprule
\usepackage{booktabs}
% for multiple authors as a block
\usepackage{authblk}

% I redefine vectors to be bold
\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

% I can define new macros for things I use a lot
\newcommand{\datapoint}{\vec{x}}
\newcommand{\weights}{\vec{w}}

\DeclareMathOperator{\argmax}{argmax}


\begin{document}

\title{Learning 2048 by Reinforcement Learning}
\author[*]{Chun Wing Wong}
\author[**]{Asbin Rai}
\author[**]{Wentao Xu}
\author[**]{Xiaowen Man}
\affil[*]{Dept. of Physics \& Astronomy}
\affil[**]{Dept. of Information Studies}
\affil[ ]{University College London, WC1E 6BT}
\date{\today}

\maketitle

\begin{abstract}
2048 is a very popular decision base game on mobile devices. The game has very simple concept and very clear targets to achieve, which makes it an interesting case for an AI to learn through reinforcement learning. We have, therefore, decided to investigate this and multiple simulations are made. Unfortunately, we are not very convinced that our method has succeeded in training a competent AI to play the game. 
\end{abstract}

\section{Introduction}
2048 has become a very popular game in the past 10 years. It has a very simple concept which involves moving the tiles around trying to achieve higher scores. As a group of people who enjoyed the game before, we have decided to attempt training an AI to play this game through pure reinforcement learning.  Multiple methods have been attempted but the results prove that 2048 perhaps is a game too complicated, despite the simplicity in the game concept, to be learnt through pure reinforcement learning. According to some online resources, it is shown that deep reinforcement learning with a 3 layer neural network is required to achieve decent results \cite{dedieu2017deep}.
\\

In the following, we will first present some background information such as a detailed explanation of the game mechanics. Then, we will present the method we used during the training process in the following section. Results will be presented after methods followed by a discussion section which will explain why we think our method has failed. 


% sections for your report can be in subfiles
\input{background}
\input{method}
\input{results}
\input{discussion}


\section*{Declaration}
This document represents the group report submission from the named authors for the project assignment of module: Foundations of Machine Learning and Data Science (INST0060), 2018-19. In submitting this document, the authors certify that all submissions for this project are a fair representation of their own work and satisfy the UCL regulations on  plagiarism.

% to put references in
\bibliography{report}
% define the bibliography style
\bibliographystyle{plain}

\end{document}
